# Sports Cards

```{problem_description}
In this experiment, the experimenters invited consumers at a sports card trading show to bid against one other bidder for a pair trading cards.  We abstract from the multi-unit-auction details here, and simply state that the treatment auction format was theoretically predicted to produce lower bids than the control auction format.  We provide you a relevant subset of data from the experiment.

In this question, we are asking you to produce p-values and confidence intervals in three different ways: 

1) Using a `t.test`; 
2) Using a regression; and,
3) Using randomization inference. 
```

```{r load cards data }
d <- fread('../data/list_data_2019.csv')
```

## t-test and confidence interval
Using a `t.test`, compute a 95% confidence interval for the difference between the treatment mean and the control mean. After you conduct your test, write a narrative statement, *using inline code evaluation* that describes what your tests find, and how you interpret these results. (You should be able to look into `str(t_test_cards)` to find the pieces that you want to pull to include in your written results.) 

```{r cards t-test, include=TRUE}
# this should be the t.test object. Extract pieces from this object 
# in-text below the code chunk.
t_test_cards <- 'fill this in'  
```

**Narrative Analysis: ...**

## Interpretation of confidence interval
In your own words, what does this confidence interval mean? This can be simple language, but it has to be statistically appropriate language. 

**Answer:** ...

## Randomization inference, and confidence interval?
Conduct a randomization inference process, with `n_ri_loops = 1000`, using an estimator that you write by hand (i.e. in the same way as earlier questions). On the sharp-null distribution that this process creates, compute the 2.5% quantile and the 97.5% quantile using the function `quantile` with the appropriate vector passed to the `probs` argument. This is the randomization-based uncertainty that is generated by your design. After you conduct your test, write a narrative statement of your test results. 

```{r cards randomization inference, include=TRUE} 
## first, do you work for the randomization inference
n_ri_loops <- 1000

cards_ate             <- 'fill this in'
cards_ri_distribution <- 'fill this in' # numeric vector of length equal 
                                        # to your number of RI permutations
cards_ri_quantiles    <- 'fill this in' # there's a built-in to pull these. 
cards_ri_p_value      <- 'fill this in'
```

**Narrative: ...**

## Compare regression and randomization inference
Do you learn anything different if you regress the outcome on a binary treatment variable? To answer this question, regress `bid` on a binary variable equal to 0 for the control auction and 1 for the treatment auction and then calculate the 95% confidence interval using *classical standard errors* (in a moment you will calculate with *robust standard errors*). There are two ways to do this -- you can code them by hand; or use a built-in, `confint`. After you conduct your test, write a narrative statement of your test results. 

```{r cards ols regression, include=TRUE}
# this should be a model object, class = 'lm'. 
mod <- 'fill this in' 
```

**Narrative: ...**

## Regression with robust confidence interval
Calculate the 95% confidence interval using robust standard errors, using the `sandwich` package. There is a function in `lmtest` called `coefci` that can help with this. It is also possible to do this work by hand. After you conduct your test, write a narrative statement of your test results.

```{r cards robust ci, include=TRUE}
# this should be a numeric vector of length 2
cards_robust_ci <- 'fill this in' 
```

**Narrative: ...**

## Compare and contrast results
Characterize what you learn from each of these different methods -- are the results contingent on the method of analysis that you choose? 

**Answer:** ...
