# What happens when pilgrims attend the Hajj pilgrimage to Mecca? 

```{problem_description}
What happens when a diverse set of people are brought together toward a common purpose? Maybe it brings people together, or maybe instead it highlights the differences between groups.  [Clingingsmith, Khwaja and Kremer (2009)](https://dash.harvard.edu/handle/1/3659699) investigate the question. by asking Pakistani nationals to provide information about their views about people from other nations. 

The random assignment and data is collected in the following way (detailed in the paper): 

- Pakistani nationals apply for a chance to attend the Hajj at a domestic bank. Saudi Arabia agreed in the time period of the study (2006) to grant 150,000 visas. 
- Of the 135,000 people who applied for a visa, 59% of those who applied were successful. 
- The remainder of the visas were granted under a different allocation method that was not randomly assigned, and so this experiment cannot provide causal evidence about other allocation mechanisms. 
- Among the 135,000 who apply, the authors conduct a random sample and survey about these respondents views about others. 

Using the data collected by the authors, test, using randomization infernece, whether there is a change in beliefs about others as a result of attending the Hajj. 

- Use, as your primary outcome the `views` variable. This variable is a column-sum of each respondents views toward members of other countries. 
- Use, as your treatment feature `success`. This variable encodes whether the respondent successfully attended the Hajj. 
```

```{r load hajj data}
d <- fread("../data/clingingsmith_2009.csv")
```

## State a null hypothesis
State the sharp-null hypothesis that you will be testing.  

```{r, include = TRUE}

```

**Answer:** ...

## Group by average
Using `data.table`, group the data by `success` and report whether views toward others are generally more positive among lottery winners or lottery non-winners. This answer should be of the form `d[ , .(mean_views = ...), keyby = ...]` where you have filled in the `...` with the appropriate functions and variables. 

```{r actual hajj ate, include = TRUE}
# the result should be a data.table with two columns and two rows
hajj_group_mean <- 'fill this in' 

# from the `hajj_group_mean` produce a single, numeric vector that is the ate. 
# check that it is numeric using `class(hajj_ate)`
hajj_ate        <- 'fill this in' 
```

**Answer:** ...

```{problem_description}
But is this a "meaningful" difference? Or, could a difference of this size have arisen from an "unlucky" randomization? Conduct 10,000 simulated random assignments under the sharp null hypothesis to find out. (Do not just copy the code from the async, think about how to write this yourself.) 
```

```{r hajj randomization inference, include=TRUE}
## do your work to conduct the randomization inference here.
## as a reminder, RI will randomly permute / assign the treatment variable
## and recompute the test-statistic (i.e. the mean difference) under each permutation
## this should be a numeric vector that has a length equal to the number 
## of RI permutations you ran
hajj_ri_distribution <- 'fill this in' 
```

## Randomization inference: At least as large
C. How many of the simulated random assignments generate an estimated ATE that is at least as large as the actual estimate of the ATE? Conduct your work in the code chunk below, saving the results into `hajj_count_larger`, but also support your coding with a narrative description. In that narrative description (and throughout), use R's "inline code chunks" to write your answer consistent with each time your run your code.  

```{r hajj one-tailed count, include = TRUE}
# length 1 numeric vector from comparison of `hajj_ate` and `hajj_ri_distribution`
hajj_count_larger <- 'fill this in' 
```

**Answer:** ...

## Randomization inference: one-sided p-value
If there are `hajj_count_larger` (`r hajj_count_larger`) randomizations that are larger than `hajj_ate` (`r hajj_ate`), what is the *one-tailed* p-value? Both write the code in the following chunk, and include a narrative description of the result following your code.  

```{r hajj one-tailed p-value, include=TRUE}
# length 1 numeric vector
hajj_one_tailed_p_value <- 'fill this in'  

```

**Answer:** ...

## Randomization inference: two-sided p-value
Now, conduct a similar test, but for a two-sided p-value. You can either use two tests, one for larger than and another for smaller than; or, you can use an absolute value (`abs`). Both write the code in the following chunk, and include a narrative description of the result following your code. 

```{r hajj two-tailed p-value, include=TRUE}
# length 1 numeric vector
hajj_two_tailed_p_value <- 'fill this in'  
```

**Answer:** ...
