# Potential Outcomes and Treatment Effects 

```{r, include = FALSE}
table <- data.table(
  subject = 1:7, 
  y_0 = c(10, 12, 15, 11, 10, 17, 16), 
  y_1 = c(12, 12, 18, 14, 15, 18, 16),
  tau = c(2, 0, 3, 3, 5, 1, 0)
)
```

## Illustration
Use the values in the table below to illustrate that $E[Y_i(1)]-E[Y_i(0)] = E[Y_i(1) - Y_i(0)]$.  

```{r, include = TRUE}
# Compute means
E_Y1 <- mean(table$y_1) # Mean of Y_i(1)
E_Y0 <- mean(table$y_0) # Mean of Y_i(0)
E_tau <- mean(table$tau) # Mean of tau

# Print results
list(
  "E[Y_i(1)]" = E_Y1,
  "E[Y_i(0)]" = E_Y0,
  "E[Y_i(1)] - E[Y_i(0)]" = E_Y1 - E_Y0,
  "E[Y_i(1) - Y_i(0)]" = E_tau
)

```

**Answer:** Thus the equality $E[Y_i(1)]-E[Y_i(0)] = E[Y_i(1) - Y_i(0)]$ holds true, with both sides equal to 2.

## Data Possibilities
Is it possible to collect all necessary values and construct a table like the one provided in real life? Explain why or why not?  

**Answer:** No, because of the fundamental problem of causal inference, which states that we cannot observe both potential outcomes $Y_i(0)$ and $Y_i(1)$ for the same individual at the same time.