# Visual Acuity 

```{problem_description}
Suppose we are interested in the hypothesis that children playing outside leads them to have better eyesight.

Consider the following population of ten children whose visual acuity we can measure. 

- Visual acuity is the decimal version of the fraction given as output in standard eye exams. 
- Someone with 20/20 vision has acuity 1.0, while someone with 20/40 vision has acuity 0.5. 
- Numbers greater than 1.0 are possible for people with better than “normal” visual acuity.
```

```{r make visual data}
d <- data.table(
  child = 1:10, 
  y_0 = c(1.2, 0.1, 0.5, 0.8, 1.5, 2.0, 1.3, 0.7, 1.1, 1.4), 
  y_1 = c(1.2, 0.7, 0.5, 0.8, 0.6, 2.0, 1.3, 0.7, 1.1, 1.4)
)
```

```{problem_description}
In this table: 

- `y_1` means the measured *visual acuity* if the child were to play outside at least 10 hours per week from ages 3 to 6  
- `y_0` means the measured *visual acuity* if the child were to play outside fewer than 10 hours per week from age 3 to age 6; 
- Both of these potential outcomes *at the child level* would be measured at the same time, when the child is 6. 
```

## Treatment effect
Compute the individual treatment effect for each of the ten children.  

```{r, include = TRUE}
# Add a column for the individual treatment effect
d[, tau := y_1 - y_0]
print(d)

```  

**Answer:** The individual treatment effects (tau) are calculated as $y_1$ - $y_2$.

## Story time
Tell a "story" that could explain this distribution of treatment effects. In particular, discuss what might cause some children to have different treatment effects than others.  

```{r, include = TRUE}
# Use this code chunk to show your code work (if needed)

```  

**Answer:** ...

## True ATE
For this population, what is the true average treatment effect (ATE) of playing outside.    

```{r, include = TRUE}
# Calculate the true average treatment effect (ATE)
true_ATE <- mean(d$tau)
print(true_ATE)

```

**Answer:** -0.03

## Even-Odd split
Suppose we are able to do an experiment in which we can control the amount of time these children play outside for three years. We happen to randomly assign the odd-numbered children to treatment and the even-numbered children to control. What is the estimate of the ATE you would reach under this assignment? (Please describe your work.)  

```{r, include = TRUE}
# Split the children into treatment (odd) and control (even)
d[, assignment := ifelse(child %% 2 == 1, "treatment", "control")]

# Calculate the observed ATE
observed_ATE <- mean(d[assignment == "treatment", y_1]) - mean(d[assignment == "control", y_0])
print(observed_ATE)

```

**Answer:** -0.06. The observed ATE under this split is calculated as the difference in means between the treatment group ($y_1$ for odd-numbered children) and the control group ($y_0$ for even-numbered children)

## Biased or Unbiased?
How different is the estimate from the truth? In your own words, why is there a difference? Does this mean that the estimator is a biased or an unbiased estimator? Does this mean that the estimate is biased or unbiased? 

```{r, include = TRUE}
# True ATE
true_ATE <- mean(d$y_1 - d$y_0)

# Even-odd split assignment
treated <- d[child %% 2 == 1] # Odd-numbered children assigned to treatment
control <- d[child %% 2 == 0] # Even-numbered children assigned to control

# Estimated ATE under even-odd split
estimated_ATE <- mean(treated$y_1) - mean(control$y_0)

# Difference between estimate and truth
bias <- estimated_ATE - true_ATE

# Output results
list(
  true_ATE = true_ATE,
  estimated_ATE = estimated_ATE,
  bias = bias
)

```

**Answer:** The estimate might differ from the true ATE due to random variation in the assignment. This does not mean the estimator is biased—it is still an unbiased estimator because the expected value of the estimate equals the true ATE.

## How many splits are possible? 
We just considered one way (odd-even) an experiment might split the children. How many different ways (every possible way) are there to split the children into a treatment versus a control group (assuming at least one person is always in the treatment group and at least one person is always in the control group)?  

```{r, include = TRUE}
# Compute the total number of possible splits
n <- 10  # Total number of children
total_splits <- sum(sapply(1:(n-1), function(k) choose(n, k)))
print(total_splits)

```

**Answer:** 1022

## Thinking about your assignment strategy
Given there are as many ways to assign as you answered in the last sub-question, can you provide a rationale for why you might prefer one assignment strategy over another? 

For concreteness, suppose that either (a) you can have a treatment assignment where one and only one of the kids is randomly assigned to treatment; or (b) you can have a treatment assignment where exactly five of the kids are randomly assigned to treatment. 

As a small hint, you might note that $\left\{\left[\displaystyle\sum_{i=1}^{n}Y_{i}(1)|d_{i}=1\right] - \left[\displaystyle\sum_{j=1}^{n}Y_{j}(0)|d_{j} = 0 \right]\right\} \equiv ATE$ is an estimator and there are some properties of estimators that we care about.  

To make the question tractable, suppose that if you were to increase the size of the population procedure (a) would keep a single kid in treatment, while procedure (b) would keep 50% of the sample in treatment and 50% of the sample in control.

**Answer:** 

A single individual in treatment leads to high variance and less reliable estimates. Assigning exactly half the sample to treatment (n/2) is generally preferable because it:
- Minimizes the variance of the estimator.
- Provides a more balanced comparison, reducing the influence of outliers.
- Ensures greater statistical power for detecting differences.

## Compute the MSE of these two designs
Because you have the entire population of kids, their entire scheduled of potential outcomes, and two proposed sampling procedures: conduct a simulation study. First, calculate all of the possible treatment effects that you might observe under each design. Then, compute the mean-squared error of each design. Which design -- the one where you have a single kid in treatment, or the one where you have five kids in treatment -- produces a lower MSE? (Hint the `combn` function might help you with your subsetting.) 

```{r, include = TRUE}
# Define functions for MSE calculation
compute_mse <- function(d, group_size) {
  combs <- combn(10, group_size)
  mse <- mean(apply(combs, 2, function(treated_idx) {
    d[, assignment := ifelse(child %in% treated_idx, "treatment", "control")]
    obs_ate <- mean(d[assignment == "treatment", y_1]) - mean(d[assignment == "control", y_0])
    (obs_ate - true_ATE)^2
  }))
  return(mse)
}

# MSE for 1 treated and 9 control
mse_1 <- compute_mse(d, 1)

# MSE for 5 treated and 5 control
mse_5 <- compute_mse(d, 5)

print(list(mse_1 = mse_1, mse_5 = mse_5))

```

**Answer:** 0.2339272, 0.08987778

## Observational study 
Suppose that we decide it is too hard to control the behavior of the children, so we do an observational study instead. Children 1-5 choose to play an average of more than 10 hours per week from age 3 to age 6, while Children 6-10 play less than 10 hours per week. Compute the difference in means from the resulting observational data.  

```{r, include = TRUE}
# Observational ATE calculation
obs_ate <- mean(d[child <= 5, y_1]) - mean(d[child > 5, y_0])
print(obs_ate)

```

**Answer:** -0.54

## Observational ATE 
Compare your answer in `Observational study` to the true ATE. In your own words what causes the difference? Does this mean that the estimator is a biased or an unbiased estimator? Does this mean that the estimate is biased or unbiased? 

```{r, include = TRUE}
# Observational ATE calculation
# Children 1-5 choose to play more than 10 hours, while 6-10 play less
obs_ate <- mean(d[child <= 5, y_1]) - mean(d[child > 5, y_0])
print(obs_ate)

```

**Answer:** 

Selection bias: Children 1-5 (who chose to play more) may systematically differ from children 6-10 in unobserved ways (e.g., initial visual acuity, genetic predispositions, environment). And the estimator is biased in this case because it does not consistently produce the true ATE due to systematic differences in the treated and untreated groups. And lastly, the specific estimate we computed here reflects that bias. It is a single realization of the biased estimator.
